\vfill A Survey of Web Testing Frameworks and a Workflow for Testing Javascript Applications

### 2014-05-12 Paper/paper.tex
More fill-in little pieces

\subsection{Contributions of This Thesis}
%- Framework
The goal of this thesis is to bring together tools that are already available for testing and combine them into a single framework that offers web application developers a single place to look for their testing needs. There are plenty of strong tools available and we hope to gather a subset of those tools to cover as much of testing spectrum as possible in an effort to save other developers time and energy in having to look at them all individually.
%- Wade through all the tools currently out there
%-- Focus in, no need to have every developer check out all 10000 tools
%-- Weigh options

%%%%%%%%%%%%%%%%%%
%%% Background 
%%% Information needed for reader to know what’s going on
%%% 	Server/Client Communication
%%% 	Cloud services
%%% 	Appropriate terms and definitions
%%%%%%%%%%%%%%%%%%
\section{Background}
In an effort to make the rest of the paper more understandable and to define the terms used in the remainder of the paper, it is useful to have a section pertaining to the different concepts and technologies surrounding the web.
If one is familiar with HTML5, JavaScript, and Testing concepts and statistics, it will likely be safe to skip this background section.

@@

\todo{Talk about GeoLocation}

\todo{TIE JS PORTION INTO THIS}

% \subsubsection{JavaScript}
JavaScript, though not the only scripting language with web use, is the primary language used to compliment HTML when making web applications. It is an interpreted language that is most often associated with client-side functionality, but in recent times has extended to the server-side. JavaScript is a prototype based object oriented scripting language with dynamic typing and first-class functions. Much of JavaScript's popularity stems from this dynamic nature that allows for quick, and often dirty, implementation of features in an iterative environment.

\todo{THIS NEEDS TO MOVE OR CHANGE SUBSECTION TO `WEB APPLICATIONS'}
\subsubsection{Node.JS}
Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.'' \cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

@@

Occasionally the cost of tools will be discussed but in general we did not review tools that did not offer a free option.
%- Free

@@

%- More setup, more flexibility.
%- Better Async support.

\paragraph{Assertion Library of Choice: Chai.js \cite{Chaijs}}
% Intentional space here
For the assertion library we chose Chai.js because it had the most flexibility for writing assertions that we'd found. It provides access to an Expect API, a Should API, and more general Assert API. The various APIs combined with Mocha's flexibilty led to a nice developer experience that can appeal to a variety of different developers.

@@

@@

%- TDD, BDD, Object methods
Intern uses Chai.js for assertion methods but has it built-in as opposed to Mocha in which the developer had to get it themselves. Again, this gives the developer access to Expect, Assert, and Object testing methods.

%- Integration with Selenium
Intern uses the WebDriver API to communicate with Selenium to drive the automated broswer testing portion of Intern.

@@

@@

The Selenium WebDriver has APIs for a variety of programming languages including: Javascript, C, Java, Python, ...

@@

Tests are written as a long chain of function calls that produce an easy-to-read series of browser events. For example, the following code segment opens a browser, goes to google.com, makes some assertions, writes ``nightwatch'' in the search box, clicks the search button, and then makes a few more assertions:
\begin{lstlisting}
module.exports = {
  "Demo test Google" : function (client) {
    client
      .url("http://www.google.com")
      .waitForElementVisible("body", 1000)
      .assert.title("Google")
      .assert.visible("input[type=text]")
      .setValue("input[type=text]", "nightwatch")
      .waitForElementVisible("button[name=btnG]", 1000)
      .click("button[name=btnG]")
      .pause(1000)
      .assert.containsText("#main", "The Night Watch")
      .end();
  }
};
\end{lstlisting}
As one can see, just reading the code line by line paints a picture of exactly what is happening and what is being checked for. The same code in straight selenium is quite a bit more verbose.

\begin{lstlisting}
var assert = require('chai').assert,
    test = require('selenium-webdriver/testing'),
    webdriver = require('selenium-webdriver');

@@

Nightwatch does not, however, support unit-testing without the browser and therefore can only be used in combination with another testing tool that supports unit-testing, such as Mocha, Jasmine, or any of the others outlined above.

>>>>

\subsection{Contributions of This Thesis}
%- Framework
The goal of this thesis is to bring together tools that are already available for testing and combine them into a single framework that offers web application developers a toolkit for their testing needs. There are plenty of strong tools available and we hope to gather a subset of those tools to cover as much of the testing spectrum as possible.

In addition to creating a single framework, we've set out to weigh the options between the most popular frameworks so that a developer need not just blindly trust our recommendations. Since every project is unique, a single set of tools cannot possibly cover the gamut. In addition to the single set of recommendations, the most popular tools are discussed so that the devloper is free to pick and choose as they see fit.
%- Wade through all the tools currently out there
%-- Focus in, no need to have every developer check out all 10000 tools
%-- Weigh options

%%%%%%%%%%%%%%%%%%
%%% Background 
%%% Information needed for reader to know what’s going on
%%% 	Server/Client Communication
%%% 	Cloud services
%%% 	Appropriate terms and definitions
%%%%%%%%%%%%%%%%%%
\section{Background}
In an effort to make the rest of the paper more understandable and to define the terms used in the remainder of the paper, we will outline the various concepts and technologies surrounding the web.
If one is familiar with HTML5, JavaScript, and Testing concepts and statistics, it will likely be safe to skip this background section.

@@

As the web is being increasingly used on mobile devices, HTML5 also introduces geolocation functionality. This funcationality requires user approval, but once that approval is gained, the web application has access to a rough idea of where the user is located. When used on devices that have GPS, such as phones and tablets, this area is more defined and a stronger lock on the user's position can be obtained. This geolocation functionality has opened the door for brand new types of web applications that can much more closely tie in with what the user is seeing or the area that they are in. For example, ads can be more targeted or an application can display distances to nearby points of interest.

JavaScript, though not the only scripting language with web use, is the primary language used to compliment HTML5 when making web applications. It is an interpreted language that is most often associated with client-side functionality, but in recent times has extended to the server-side. JavaScript is a prototype based object oriented scripting language with dynamic typing and first-class functions. Much of JavaScript's popularity stems from this dynamic nature that allows for quick, and often dirty, implementation of features in an iterative environment.

%\todo{THIS NEEDS TO MOVE OR CHANGE SUBSECTION TO `WEB APPLICATIONS'}
\paragraph{Node.JS}
As a quick aside, it will be useful to have information about Node.JS as it is used in the sample application and the evaluation applicaiton. Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.'' \cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

@@

Occasionally the cost of tools will be discussed but in general we did not review tools that only offered paid options.
%- Free

@@

Overall Mocha offered more flexibilty at the cost of additional setup and better asynchronous support. This increased flexibility came in the way of being able to select our own assertion library so that our tests looked the way we wanted them. The cost of that was the need to find our own assertion library among the dozen that are out there. We prefer Mocha's method of asynchronous testing because it required considerably less typing on our part and was more easy to follow and read than a chain of method calls.

\paragraph{Assertion Library of Choice: Chai.js \cite{Chaijs}}
For the assertion library we chose Chai.js.  It offers the most flexibility for writing assertions that we'd found. It provides access to an Expect API, a Should API, and a more general Assert API. The Expect API provides assertions in the form of ``expect(myVar).to.equal(10);'' or ``expect(myArr).to.have.length(10);''. The Should API has assertions of the form ``myVar.should.be.a(\'number\');'' or ``myArr.should.have.length(10);''. Finally, the Assert API has the more tried and true ``assert.equal(myVar, 10);'' and ``assert.lengthOf(myArr, 10);''. The various APIs combined with Mocha's flexibilty led to a nice developer experience that can appeal to a variety of different developers.

@@

QUnit was a particularly strong contender when we saw the table that was produced after running the tests but its shortcomings led us to keep looking elsewhere. QUnit's handling of asynchronous tests is nice because they are more explicitly stated for the casual read-through instead of an extra parameter or set of functions within the test itself.

@@

%- TDD, BDD, Object methods
Intern uses Chai.js for assertion methods but has it built-in as opposed to Mocha in which the developer had to get it themselves. This gives the developer access to Expect, Assert, and Intern's Object testing methods.

\todo{Add test code here!}

%- Integration with Selenium
Intern uses the WebDriver API to communicate with Selenium to drive the automated broswer testing portion of Intern. Selenium and the WebDriver API will be discussed in more detail in the next section ``Browser and UI Testing''.

@@

Intern offered a one-stop shop for all of our testing needs but fell short when it came to configuring it for our Node.js server setup. If we had a more traditional web application setup with a seperate server that served normal HTML pages, Intern.io would have likely been our go-to tool for all of our testing needs.

@@

The Selenium WebDriver has APIs for a variety of programming languages including: Javascript, C, Java, and Python.

@@

Tests are written as a long chain of function calls that produce an easy-to-read series of browser events. For example, the following code segment opens a browser, goes to google.com, makes some assertions, writes ``nightwatch'' in the search box, clicks the search button, and then makes a few more assertions:
\begin{lstlisting}
module.exports = {
  "Demo test Google" : function (client) {
    client
      .url("http://www.google.com")
      .waitForElementVisible("body", 1000)
      .assert.title("Google")
      .assert.visible("input[type=text]")
      .setValue("input[type=text]", "nightwatch")
      .waitForElementVisible("button[name=btnG]", 1000)
      .click("button[name=btnG]")
      .pause(1000)
      .assert.containsText("#main", "The Night Watch")
      .end();
  }
};
\end{lstlisting}
As one can see, just reading the code line by line paints a picture of exactly what is happening and what is being checked for.

The same code in normal Selenium is quite a bit more verbose:
\begin{lstlisting}
var assert = require('chai').assert,
    test = require('selenium-webdriver/testing'),
    webdriver = require('selenium-webdriver');

@@
